Simulation Learning in Computer Hex

### 2011-08-19 thesis/thesis.tex
Starting on problem statement and solution.

\chapter{Solution}\label{solution}

>>>>

\chapter{Solution}\label{solution}
After each move, a random move is selected in the 6-connected local area. This move is used as the next move in the playout. All subsequent moves will also have their local area examined for a random response. If all 6 connected vertices are non-empty, a move is played using the uniform random policy (the \emph{default} policy). In the uniform local variation, a response is chosen uniformly from any empty moves in the local area. The uniform local variation with tenuki is similar, but there is a probability $p=\frac{1}{6}$ of using the default policy. The learned local variation assigns a weight to each empty local vertex based on the local area. These weights are used to stochastically bias the local response. The weights are trained over time through self-play using Evolution Strategies.
